\addcontentsline{toc}{chapter}{Bibliography}

\begin{thebibliography}{9}

%  Chapter 1
\bibitem{dir19}
  Dries, L., Heijman, W., Jongeneel, R., Purnhagen, K., \& Wesseler, J. (Eds.). (2019). 
  \emph{EU Bioeconomy Economics and Policies: Volume II. Cham}, UK: Springer International Publishing.

\bibitem{bre00}
  J. Brezmes, E. Llobet, X. Vilanova, G. Saiz, and X. Correig, Fruit ripeness monitoring using an electronic nose, 
  \emph{Sensors and Actuators B-Chem Journal}, vol.69, no.3, pp.223--229, Elsevier, 2000.

\bibitem{may11}
  Z. May and M. H. Amaran, Automated ripeness assessment of oil palm fruit using RGB and fuzzy logic technique", 
  \emph{InProc. of the 13th WSEAS international conference on Mathematical and computational methods in science and engineering (MACMESE'11),}
  Stevens Point, Wisconsin, USA, pp.52--59, World Scientific and Engineering Academy and Society (WSEAS), 2011.

\bibitem{mah21}
  Mahmudul Hassan, S. K., \& Kumar Maji, A. (2021). Identification of plant species using deep learning. 
  \emph{In Proceedings of International Conference on Frontiers in Computing and Systems}
  (pp. 115-125). Springer, Singapore

  % Chapter 2
\bibitem{var20}
  B. K. Varghese, A. Augustine, J. M. Babu, D. Sunny, and E. S. Cherian. 
  \emph{Infoplant: Plant recognition using convolutional neural networks.} 
  In 2020 Fourth International Conference on Computing Methodologies and 
  Communication (ICCMC), pages 800807. IEEE, 2020.

\bibitem{rai20}
  S. A. Riaz, S. Naz, and I. Razzak. 
  \emph{Multipath deep shallow convolutional networks 
  for large scale plant species identification in wild image.}
  In 2020 International Joint Conference on Neural Networks (IJCNN), pages 17. IEEE, 2020.

\bibitem{kay19}
  Kaya, A., Keceli, A. S., Catal, C., Yalic, H. Y., Temucin, H., \& Tekinerdogan, B. (2019). 
  \emph{Analysis of transfer learning for deep neural network based plant classification models.}
  Computers and electronics in agriculture, 158, pages 20--29.

\bibitem{man19}
  Manasa, N., Herur, P., Shetty, P., Prarthana, N., \& Venkatrao, P. (2019, June). 
  \emph{Plant recognition using watershed and convolutional neural network.}
  In 2019 3rd International conference on Electronics, Communication and Aerospace Technology 
  (ICECA) (pp. 969--973). IEEE.

\bibitem{bei18}
  Beikmohammadi, A., \& Faez, K. (2018, December).
  \emph{Leaf classification for plant recognition with deep transfer learning.}
  In 2018 4th Iranian Conference on Signal Processing and Intelligent Systems
  (ICSPIS) (pp. 21--26). IEEE.

\bibitem{wan21}
  Wang, P., Niu, T., Mao, Y., Zhang, Z., Liu, B., \& He, D. (2021). 
  \emph{Identification of Apple Leaf Diseases by Improved Deep Convolutional Neural Networks With an Attention Mechanism.} 
  Frontiers in Plant Science, 1997.

\bibitem{yu21}
  Yu, H., Liu, J., Chen, C., Heidari, A. A., Zhang, Q., Chen, H., ... \& Turabieh, H. (2021). 
  \emph{Corn leaf diseases diagnosis based on K-means clustering and deep learning.} 
  IEEE Access, 9, 143824-143835.

\bibitem{wan2_21}
  Wang, G., Yu, H., \& Sui, Y. (2021). 
  \emph{Research on Maize Disease Recognition Method Based on Improved ResNet50.} 
  Mobile Information Systems, 2021.

\bibitem{ji20}
  Ji, M., Zhang, L., \& Wu, Q. (2020). 
  \emph{Automatic grape leaf diseases identification via UnitedModel based on multiple convolutional neural networks.} 
  Information Processing in Agriculture, 7(3), 418--426.

\bibitem{tha20}
  Thakur, R., Suryawanshi, G., Patel, H., \& Sangoi, J. (2020, May). 
  \emph{An innovative approach for fruit ripeness classification.} 
  In 2020 4th International Conference on Intelligent Computing and 
  Control Systems (ICICCS) (pp. 550-554). IEEE.

\bibitem{sha20}
  Shao, Y., Wang, Y., Xuan, G., Gao, Z., Hu, Z., Gao, C., \& Wang, K. (2020). 
  \emph{Assessment of strawberry ripeness using hyperspectral imaging.} 
  Analytical Letters, 54(10), 1547-1560.

  % Chapter 3
\bibitem{una20}
  \"Unal, Z. (2020). 
  \emph{Smart farming becomes even smarter with deep learning—a bibliographical analysis.} 
  IEEE Access, 8, 105587-105609.

\bibitem{has18}
  Hassoon, I. M., Kassir, S. A., \& Altaie, S. M. (2018). 
  \emph{A review of plant species identification techniques.} 
  Int Jour Sci Res, 7(8), 2319-7064.

\bibitem{moh16}
  Mohanty, S. P., Hughes, D. P., \& Salathé, M. (2016). 
  \emph{Using deep learning for image-based plant disease detection.} 
  Frontiers in plant science, 7, 1419.

\bibitem{mas21}
  Masmoudi, I., \& Lghoul, R. (2021). 
  \emph{A Deep Convolutional Neural Network Approach for Plant Leaf Segmentation and Disease Classification in Smart Agriculture.} 
  In Intelligent Computing (pp.1044--1055). Springer, Cham.

\bibitem{esr20}
  Esraa El-hariri. PhD Fayoum Universty  (2020). 
  \emph{Prediction\_Technique\_for\_Historical\_Heritage\_Preservation\_Based\_on\_IoT-8-3-166-1.}

\bibitem{alz21}
  Alzubaidi, L., Zhang, J., Humaidi, A. J., Al-Dujaili, A., Duan, Y., Al-Shamma, O., ... \& Farhan, L. (2021). 
  \emph{Review of deep learning: Concepts, CNN architectures, challenges, applications, future directions.} 
  Journal of big Data, 8(1), 1-74.

\bibitem{rat18}
  Rathi, D. (2018). 
  \emph{Optimization of transfer learning for sign language recognition targeting mobile platform.} 
  arXiv preprint arXiv:1805.06618.

\bibitem{sam19}
  Sam, S. M., Kamardin, K., Sjarif, N. N. A., \& Mohamed, N. (2019). 
  \emph{Offline signature verification using deep learning convolutional neural network (CNN) architectures GoogLeNet inception-v1 and inception-v3.} 
  Procedia Computer Science, 161, 475-483.

\bibitem{bar19}
  Barker, M. (2019). 
  \emph{Inception V3 Deep Convolutional Architecture For Classifying Acute Myeloid/Lymphoblastic Leukemia.} 
  intel. com.

\bibitem{dem19}
  Demir, A., Yilmaz, F., \& Kose, O. (2019, October). 
  \emph{Early detection of skin cancer using deep learning architectures: resnet-101 and inception-v3.}
  In 2019 medical technologies congress (TIPTEKNO) (pp. 1--4). IEEE.

\bibitem{gar21}
  Garg, A., \& Tyagi, S. (2021). 
  \emph{IoT-a supportive system for solving issues related to medical monitoring.} 
  Computational Intelligence and Predictive Analysis for Medical Science: A Pragmatic Approach, 6, 53.

\bibitem{rib19}
  Ribani, R., \& Marengoni, M. (2019, October). 
  \emph{A survey of transfer learning for convolutional neural networks.} 
  In 2019 32nd SIBGRAPI conference on graphics, patterns and images tutorials (SIBGRAPI-T) (pp. 47--57). IEEE.

\bibitem{v7lab}
\url{https://www.v7labs.com/blog/transfer-learning-guide}.


\end{thebibliography}
